Labeled object representation and manipulation with ITK

### 2007-06-11 article/Article.tex
add a word about the threading support and the inplace filtering
darcs-hash:20070611093626-2fc9d-6e718455db9ff810aa8e2be28d4f551b65d2e9c1.gz

No attribute are stored in this class, which can thus be see as the base class
for the abjects with some attributes, or which can be used when no attributes
are required.

@@

Finally, it has been chosen to develop a specific filter for the morphological
reconstruction. It would have been possible to implement the reconstruction
with the most common case (build the object collection, valuate the attributes
filter the object, and rebuild the image), but for more efficiency, the reconstruction
filter filters the collection directly, without giving them an attribute.

@@

@@

\section{Future work}

@@

@@

@@

% \url{http://www.itk.org}
% \code{Insight/Documentation/Style.pdf}
% \section{Principles of Solar Spot Detection}
% \cite{ITKSoftwareGuide}.
% \doxygen{ImageToImageFilter}

% \small \begin{verbatim}
% \end{verbatim} \normalsize

% The {itemize} environment uses a bullet for each \item.  If you want the 
% \item's numbered, use the {enumerate} environment instead.
% \begin{itemize}
%   \item  Insight Toolkit 2.4.
%   \item  CMake 2.2
% \end{itemize}

% \ref{cthead1}

\begin{figure}[htbp]
\centering
\includegraphics{cthead1}
\caption{The input image.\label{cthead1}}
\end{figure}

>>>>

No attribute are stored in this class, which can thus be see as the base class
for the objects with some attributes, or which can be used when no attributes
are required.

@@

Finally, it has been chosen to develop a specific filter for the morphological
reconstruction. It would have been possible to implement the reconstruction
with the most common case (build the object collection, valuate the attributes
filter the object, and rebuild the image), but in order to make it compatible
with the {\em ShapeLabelObject} and {\em StatisticsLabelObject}, the reconstruction
filter filters the collection directly, without setting an attribute in the objects.

@@

\section{Threading support}

When possible, the filters provided with that contribution have been multithreaded.
Some of them however, are not (easily) threadable (the {\em KeepNObjects} and {\em Relabel}
filters), are shouldn't get any performance improvement in a threaded version
(the {\em Opening} filters).

The {\em BinaryImageToLabelCollectionImageFilter} class is a slight modification of the
Richard Beare's {\em ConnectedComponentImageFilter}, and thus, has not been threaded.
It should however be possible to increase its performance that way.

The classical thread architecture is used when the input image is an {\em Image}: the image
is splitted in several regions (one per thread), and each thread work on its own region.

Because the {\em LabelCollectionImage} image is not an array of pixels, it can't be splitted
that way. Instead, several threads are created, and try to take an object in the collection.
If they get one, they process that object individually, and try to get another one when the
object is processed. If no object can be get, the thread ends. A {\em FastMutexLock} is used
to ensure that only one thread take an object at a time.

For the developer, the usage of the threading support is made very simple, by subclassing
{\em LabelCollectionImageFilter}, or {\em InPlaceLabelCollectionImageFilter}, and implementing
the method {\em virtual void ThreadedGenerateData( LabelObjectType * labelObject )} in the
new class. This method only has to process the labelObject passed in parameter. All the
threading code and mutex lock management is already implemented. The mutex lock remain
accessible if the subclass need to use it, as the {\em m\_LabelObjectContainerLock} ivar.

\section{In place filtering}

All the filters which are taking a {\em LabelCollectionImage} as input, and are producing a {\em LabelCollectionImage} as output, are implemented as a subclass of {\em InPlaceLabelCollectionImageFilter} and
thus are running in place by default.

The use can modify this behavior with the {\em SetInPlace( bool )}, {\em InPlaceOn()}, and {\em InPlaceOff()} methods, as with the usual {\em InPlaceImageFilter}.

To use that feature, a developer only have to subclass {\em InPlaceLabelCollectionImageFilter} and
implement the {\em virtual void ThreadedGenerateData( LabelObjectType * labelObject )}, to get easy thread
support (see the previous section), or the {\em virtual void GenerateData()} if the filter is not threadable. In that last case,
the only image to manipulate is the one get with the {\em GetOutput()} method, which is the input image if the filter runs in place, or a copy of the input image if the filter is not running in place.

@@

\section{Performance}

TODO

\section{Known bugs and future work}

@@

The computation of the moments is partially implemented. The help of someone with a good knownledge of that subject would be very helpful to complete that work. The moments for the binary shape shoudl also be implemented.

@@

The {\em BinaryImageToLabelCollectionImageFilter} class should be threaded to get the best of that filter on multiprocessors systems.

@@

ITK is currntly lacking a good way to manipulate the binary objects. That contribution I hope to have mostly
filled that lack.
